Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-09-03 paper/main.tex
more paper skeleon

\IEEEPARstart{T}{his} demo file is intended to serve as a ``starter file''
for IEEE Computer Society journal papers produced under \LaTeX\ using
IEEEtran.cls version 1.8b and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.
\section{Related Work}
\subsection{Continuity}
\begin{figure}[!t]
  \includegraphics[width=2.5in]{k_different_types.png}
\end{figure}
\cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989}
\subsection{Equivariance}
\begin{figure}[!t]
  \includegraphics[width=2.5in]{equiv.png}
\end{figure}

\subsection{Category Theory}

\section{Topological Equivariant Artist Model}
%%- brief intro to artist in most simple form $\A\rightarrow H$

\subsection{Data Bundle \dtotal}
\begin{figure}[!t]

\end{figure}
\paragraph{Continuity: Base Space \dbase}
\paragraph{Equivariance: Fiber \dfiber}
\paragraph{Structured Data: Section \dsection}
\subsubsection{Continuity of Data: sheaf $\mathcal{O}$}
\begin{figure}
  \includegraphics[width=2.5in]{sheaf.png}
  \caption{Maybe create a figure that shows what the sheaf does, like 
  https://www.euclideanspace.com/maths/topology/sheaf/index.htm}
\end{figure}
\subsection{Visual Bundle \gtotal} %probably doesn't all need to be subsections, just figure + short description
\begin{figure}
  \includegraphics[width=2.5in]{render.png}
\end{figure}
\paragraph{Continuity: Base Space \gbase}
\paragraph{Equivariance: Fiber \gfiber}
\paragraph{Structured Data: Visual \gsection}
\subsection{Artist}
%% flesh out categorical framing of artist, walk through how eq 16 is part of implementing the artists
%% https://github.com/story645/proposal/blob/main/notes/meetings/2021_08_30.md

\subsubsection{Visual to Data: \vindex}
\begin{figure}[!t]
  \includegraphics[width=2.5in]{xi.png}
\end{figure}
\subsubsection{Representation Bundle: \vtotal}

\subsubsection{Data to Representation: \vchannel} %look at what K&S call these stages
\begin{figure}[!t]
  \includegraphics[width=2.5in]{nu.png}
\end{figure}

\subsubsection{Representation to Visual: \vmark} % look at what K&S call these stages
\begin{figure}[!t]
  \includegraphics[width=2.5in]{q.png}
\end{figure}

\begin{figure}[!t]
  \includegraphics[width=2.5in]{path_of_q.png}
  \caption{rework this as a commutative box w/ the r in E row associated w/ this qhat(k)}
\end{figure}

\subsection{Combining Artists}
\begin{figure}[!t]
\centering
\subfloat[Artists with shared $\mu_i$ renderered correctly]{\includegraphics[width=2.5in]{combined_artist.png}%
\label{fig_first_case}}
\hfil
\subfloat[Artists without shared $\mu_i$]{\includegraphics[width=2.5in]{exploding_artist.png}%
\label{fig_second_case}}
\caption{Simulation results for the network.}
\label{fig_sim}
\end{figure}

\section{Case Study}

@@

\appendices
\section{Rendering: \gsection}
\section{Manufacturing $\vmarkd \leftarrow \vmark$}

% you can choose not to have a title for an appendix
% if you want by leaving the argument blank
\section{}
Appendix two text goes here.

>>>>

\IEEEPARstart{T}{his} demo file is intended to serve as a ``starter file''
for IEEE Computer Society journal papers produced under \LaTeX\ using
IEEEtran.cls version 1.8b and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.
\section{Related Work}
\subsection{Describe API w/ Category Theory}
\begin{equation}
  \label{eq:artist}
  \mathscr{\vartist}: \mathscr{\dtotal} \rightarrow \mathscr{\gtotal}
\end{equation}

\subsection{Continuity}
Continuity is
\begin{figure}[!h]
  \includegraphics[width=2.5in]{k_different_types.png}
\end{figure}

We care about continuity b/c 
\begin{figure}
  \includegraphics[width=2.5in]{whycontinuity.png}
\end{figure}

We express continuity using fiber bundles, which are ...
\cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989}
\begin{equation}
  \label{eq:fiber_bundle}
  \begin{tikzcd}
      \dfiber \arrow[r, hook] & \dtotal \arrow[r, "\pi"] & \dbase
  \end{tikzcd}
\end{equation}

\subsection{Equivariance}
What is it?

\begin{figure}[!h]
  \includegraphics[width=2.5in]{equiv.png}
\end{figure}

\begin{tikzcd}
  data \arrow[r] \arrow[d, "function"] & representation \arrow[r] & visual\;stimulus \arrow[d, "visual\;equivalent\;to\;function"] \\
  data \arrow[r]                       & representation \arrow[r] & visual\; stimulus                                          
\end{tikzcd}

\section{Topological Equivariant Artist Model}
%%- brief intro to artist in most simple form $\vartist \dtotal \rightarrow \gtotal$

\section{Union of Artists}
\begin{figure}[!h]
\centering
\subfloat[Artists with shared $\mu_i$ renderered correctly]{\includegraphics[width=1.2in]{combined_artist.png}%
\label{fig_first_case}}
%\hfil
\subfloat[Artists without shared $\mu_i$]{\includegraphics[width=1.2in]{exploding_artist.png}%
\label{fig_second_case}}
\caption{Simulation results for the network.}
\label{fig_sim}
\end{figure}
}

\subsection{Data Bundle \dtotal}
\begin{figure}[!h]
  \includegraphics[width=2.5in]{k_qspace.png}
  \caption{this is gonna be replaced w/ more concrete}
\end{figure}

\paragraph{Structured Data: Section \dsection}
\begin{equation}
  \begin{tikzcd}
      \dfiber \arrow[r, hook] & \dtotal \arrow[d, "\pi"'] \\
                        & \dbase \arrow[u, "\dsection"', bend right]
  \end{tikzcd}
\end{equation}

\paragraph{Structure: Continuity and Equivariant Actions}
\begin{equation}
  \begin{tikzcd}
      \dfiber_i \arrow[d, "m_j"'] \arrow[rd, "m_j\;\circ\; m_k"] &         \\
      \dfiber_i \arrow[r, "m_k"']  & \dfiber_i
  \end{tikzcd}
\end{equation}

\subsubsection{Continuity of Data: sheaf \sheaf}
\begin{figure}
  \includegraphics[width=2.5in]{sheaf.png}
  \caption{Maybe create a figure that shows what the sheaf does, like 
  https://www.euclideanspace.com/maths/topology/sheaf/index.htm}
\end{figure}

\subsection{Graphic Bundle \gtotal} %probably doesn't all need to be subsections, just figure + short description
\begin{figure}
  \includegraphics[width=2.5in]{render.png}
\end{figure}
\begin{equation}
  \begin{tikzcd}[ampersand replacement=\&]
      \gfiber \arrow[r, hook] \& \gtotal \arrow[d, "\pi"'] \\
                        \& \gbase \arrow[u, "\gsection"', bend right]
  \end{tikzcd}
\end{equation}
\paragraph{Continuity: Base Space \gbase}
\paragraph{Equivariance: Fiber \gfiber}
\paragraph{Structured Data: Visual \gsection}

\subsection{Artist}
%% flesh out categorical framing of artist, walk through how eq 16 is part of implementing the artists
%% https://github.com/story645/proposal/blob/main/notes/meetings/2021_08_30.md
\begin{equation}
  \vartist: \sheaf(\dtotal) \rightarrow \sheaf(\gtotal)
  \label{eq:math:artist:artist}
\end{equation}

\subsubsection{Graphic to Data: \vindex}
\begin{figure}[!h]
  \includegraphics[width=2.5in]{xi.png}
\end{figure}
\begin{equation}
  \begin{tikzcd}
      \dtotal \arrow[d, "\pi"'] & \gtotal \arrow[d, "\pi"'] \\
      \dbase                   & \gbase \arrow[l, "\vindex"']
  \end{tikzcd}
  \label{eq:math:graphic:vindex}
\end{equation}

\begin{equation}
  \label{eq:math:artist:diagram}
  \begin{tikzcd}
      \dtotal \arrow[r, "\vchannel"] \arrow[rd, "\pi"'] & \vtotal \arrow[d, "\pi"] & \vindex^*\vtotal \arrow[r, "\vmark"] \arrow[d, "\vindex^*\pi"'] \arrow[l, "\vindex^*"'] & \gtotal \arrow[ld, "\pi"] \\
                                            & \dbase                  & \gbase \arrow[l, "\vindex"']                                              &                    
      \end{tikzcd}
\end{equation}

\subsubsection{Representation \vtotal}
\begin{equation}
  \begin{tikzcd}[ampersand replacement=\&]
      \vfiber \arrow[r, hook] \& \vtotal \arrow[d, "\pi"'] \\
                        \& \dbase \arrow[u, "\vsection"', bend right]
  \end{tikzcd}
\end{equation}

\subsubsection{Data to Representation: \vchannel} %look at what K&S call these stages
\begin{figure}[!h]
  \includegraphics[width=2.5in]{nu.png}
\end{figure}
\begin{equation}
  \label{eq:math:artist:nu}
  \{\vchannel_{0}, \ldots, \vchannel_{n}\}: \{\dsection_{0}, \ldots, \dsection_{n}\} \mapsto \{\vsection_{0}, \ldots, \vsection_{n}\}
\end{equation}

We enforce the equivariance constraint
\begin{equation}
  \label{eq:math:artist:nu_commute}
\begin{tikzcd}
  \dtotal_i \arrow[r] \arrow[r, "\vchannel_i"] \arrow[d, "m_{\delement}"'] & \vtotal_i \arrow[d, "m_{\velement}"] \\
  \dtotal_i \arrow[r, "\vchannel_i"]                           & \vtotal_i               
\end{tikzcd}
\end{equation}

\subsubsection{Representation to Visual: \vmark} % look at what K&S call these stages

\begin{figure}[!h]
  \includegraphics[width=2.5in]{q.png}
\end{figure}

\begin{figure}[!h]
  \includegraphics[width=2.5in]{diff_type_q.png}
  \caption{rework this as a commutative box w/ the r in E row associated w/ this qhat(k)}
\end{figure}

\subsubsection{Data $\leftrightarrow$ Visual}
Putting all the pieces together, we have a system for 
\begin{equation}
  \label{eq:math:artist:diagram}
  \begin{tikzcd}
      \dtotal \arrow[r, "\vchannel"] \arrow[rd, "\pi"'] & \vtotal \arrow[d, "\pi"] & \vindex^*\vtotal \arrow[r, "\vmark"] \arrow[d, "\vindex^*\pi"'] \arrow[l, "\vindex^*"'] & \gtotal \arrow[ld, "\pi"] \\
                                            & \dbase                  & \gbase \arrow[l, "\vindex"']                                              &                    
      \end{tikzcd}
\end{equation}

\section{Case Study}
\begin{figure}[t!]
  \includegraphics[width=2.5in]{path_of_q.png}
    \caption{add in xi!}
  \label{fig:api}
\end{figure}
We implement the \texbf{arrows} in \autoref{fig:api}

@@

\appendices
\section{Rendering: \gsection}
\section{Manufacturing $\vmarkd \leftarrow \vmark$}
\begin{equation}
  \begin{tikzcd}
      \textcolor{gray!50}{\dtotal} \arrow[r, "\vchannel", color=gray!50] \arrow[rd, "\pi"', color=gray!50] & \vtotal \arrow[d, "\pi"']                  & \vindex^*\vtotal \arrow[r, "\vmark", color=gray!50] \arrow[d, "\vindex^*\pi"'] \arrow[l,  "\vindex^*"'] & \textcolor{gray!50}{\gtotal} \arrow[ld, "\pi", color=gray!50] \\ & \dbase \arrow[u, "\vsection"', bend right] & \gbase \arrow[l, "\vindex"'] \arrow[u, "\vindex^*\vsection"', bend right]               &                          
      \end{tikzcd}
      \label{eq:math:artist:qhat}
\end{equation}
